Topological Sigma Models for Generalized Para-Complex Geometry

### 2020-01-20 newdraft.tex
few more comments to address

\brian{Symplectic form}

@@

\brian{Hamiltonians and action functional}

@@

This formalism can be made explicit in the case of the $3D$/$2D$ system. \brian{finish}

@@

\brian{define $\omega_{\KK}$ see Appendix A of \cite{Cattaneo:2009zx}.}

\begin{proposition}\label{prop: symp}
Suppose $\KK$ is a generalized para-complex structure on a Courant algebroid $E$.
Then, there are symplectomorphisms of $2$-shifted symplectic dg manifolds
\[
\left(T^*[2] \Tilde{L}, \omega_{\KK} \right) \cong X_E \cong \left(T^*[2] \overset{\;}{L}, \Tilde{\omega}_{\KK} \right) .
\]
\end{proposition}
\begin{proof}
The proof is completely analogous to the proofs of the results in Appendix A of \cite{Cattaneo:2009zx}.
\end{proof}

@@

@@

\brian{below needs to be fixed up a bit}

@@

@@

\hrulefill

\brian{***para Kahler example, **example where the paracomplex structures commute but are not equal (this is where people see ``twisted chiral"), para version of T-duality, **Poisson $\sigma$-model, going back and forth between generalized (para) complex.
}

\brian{Case of para structure on $M \times M$. Two copies of $BF$ theory.}

\subsection{Para holomorphic variants}

>>>>

\brian{Introduce symplectic form}

@@

\brian{Hamiltonians and action functional. This is just more review and citations.}

@@

This formalism can be made explicit in the case of the $3D$/$2D$ system. \brian{I basically do this already below, but I might add some filler statements here.}

@@

\brian{define $\omega_{\KK}$ see Appendix A of \cite{Cattaneo:2009zx}. 
If dbro is OK, I say we just translate his result and cite it. The proof seems to follow immediately.}
\begin{proposition}\label{prop: symp}
Suppose $\KK$ is a generalized para-complex structure on a Courant algebroid $E$.
Then, there are symplectomorphisms of $2$-shifted symplectic dg manifolds
\[
\left(T^*[2] \Tilde{L}, \omega_{\KK} \right) \cong X_E \cong \left(T^*[2] \overset{\;}{L}, \Tilde{\omega}_{\KK} \right) .
\]
\end{proposition}
\begin{proof}
The proof is completely analogous to the proofs of the results in Appendix A of \cite{Cattaneo:2009zx}.
\end{proof}

@@

\begin{proof}
The BRST operator is of the form $\d_{dR} + Q$ where $Q$ is a degree $+1$ vector field on the target and $\d_{dR}$ is the de Rham differential on $\Sigma$.  
Locally, the BRST cohomology reduces to the cohomology of functions on the target graded manifold equipped with differential $Q$.
In each case at hand, the target is of the form $L[1]$ with differential $Q = \d_L$.
\end{proof}

@@

\btd{I'm getting snagged on this a bit. 
What I want to show is that the full theory has as its BRST cohomology the complex I describe below. 
Do you see how this works?
}

@@

%\brian{Case of para structure on $M \times M$. Two copies of $BF$ theory.}

\subsection{Anomalies and para holomorphic variants}

@@

%\brian{***para Kahler example, **example where the paracomplex structures commute but are not equal (this is where people see ``twisted chiral"), para version of T-duality, **Poisson $\sigma$-model, going back and forth between generalized (para) complex.
%}
